Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-27 analysis/paper/hotspots-paper.Rmd
updated Rmd; replaced latex eqns with pandoc eqns

\begin{equation}
vec(Y) = X vec(B) + vec(G) + vec(E)
\label{eq:mvlmm}
\end{equation}

\begin{equation}
G \sim MN_{n x 2}(0, K, V_g)
\end{equation}

\begin{equation}
E \sim MN_{n x 2}(0, I_n, V_e)
\end{equation}

@@

\begin{equation}
\hat B = (X^T\hat \Sigma^{-1}X)^{-1}X^T\hat\Sigma^{-1}Y
\label{eq:Bhat}
\end{equation}

\begin{equation}
\hat \Sigma = \hat V_g \otimes \hat K + \hat V_e \otimes I_n
\label{eq:Sigmahat}
\end{equation}

\begin{equation}
l_{10}(\hat B, \hat \Sigma) = - \frac{1}{2}\log_{10}\left((Y - X\hat B)^T\hat \Sigma^{-1}(Y - X\hat B)\right) - n\log_{10}(2\pi) - \log_{10}|\hat \Sigma|
\label{eq:loglik}
\end{equation}

@@

\begin{equation}
LOD = \log_{10} \left(\frac{\max_{\lambda_1, \lambda_2}L(B, \Sigma, \lambda_1, \lambda_2)}{\max_{\lambda}L(B, \Sigma, \lambda, \lambda)} \right)
\label{eq:lrt}
\end{equation}

\begin{equation}
ll(\lambda_1, \lambda_2)
\end{equation}

@@

\begin{equation}
Y = \alpha 1 + WC + E
\label{model1}
\end{equation}

\begin{equation}
Y = XB + WC + E
\label{model2}
\end{equation}

\begin{equation}
Y = \alpha 1 + WC + M\beta + E
\label{model3}
\end{equation}

\begin{equation}
Y = XB + WC + M\beta + E
\label{model4}
\end{equation}

@@

scols_pre <- scols_extra %>%
  dplyr::select(n_med_per_local$local_symbol)
# get ordering for columns of scols_pre
col_order <- scols_pre %>%
  t() %>%
  dist() %>%
  hclust() %>%
  as.dendrogram() %>%
  dendextend::seriate_dendrogram(dist(t(scols_pre))) %>%
  order.dendrogram()
scols <- scols_pre[ , col_order] %>%
  mutate(local = scols1)
```

```{r heat9-2}
ord <- match(rn, rownames(pm))

p <- pm[ord, ord] %>%
  apply(FUN = trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply(Rowv = FALSE,
            Colv = FALSE,
            cexRow = 0.2,
            cexCol = 0.2,
            symm = TRUE,
            row_side_colors = scols[ord, ],
            col_side_colors = tibble(local = scols1[ord]),
            limits = c(0, 5)
            ) %>%
  hide_guides()
fnhtml <- here("analysis", "figures", paste0("Chr", hot_chr, "hm.html"))
fnpdf <- here("analysis", "figures", paste0("Chr", hot_chr, "hm.pdf"))
htmlwidgets::saveWidget(widget = p,
                        file = fnhtml
                        )
webshot::webshot(url = fnhtml,
                 file = fnpdf,
                 cliprect = "viewport"
                 )
```

@@

```{r heat9-5, ref.label = "heat9-2"}
```

```{r hm_plot-5, ref.label = "hm_plot-2"}
```

@@

```{r heat9-7, ref.label = "heat9-2"}
```

```{r hm_plot-7, ref.label = "hm_plot-2"}

```

@@

```{r heat9-11, ref.label = "heat9-2"}
```

```{r hm_plot-11, ref.label = "hm_plot-2"}

```

@@

```{r heat9-13, ref.label = "heat9-2"}
```

```{r hm_plot-13, ref.label = "hm_plot-2"}

```

@@

```{r def-2}
hot_chr <- 2
```

```{r fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 2 hotspot."}
#include_graphics(paste0("../figures/Chr", hot_chr, "_scatter.pdf"))
```

>>>>

$$
vec(Y) = X vec(B) + vec(G) + vec(E)
\label{eq:mvlmm}
$$

$$
G \sim MN_{n x 2}(0, K, V_g)
$$

$$
E \sim MN_{n x 2}(0, I_n, V_e)
$$

@@

$$
\hat B = (X^T\hat \Sigma^{-1}X)^{-1}X^T\hat\Sigma^{-1}Y
\label{eq:Bhat}
$$

$$
\hat \Sigma = \hat V_g \otimes \hat K + \hat V_e \otimes I_n
\label{eq:Sigmahat}
$$

$$
l_{10}(\hat B, \hat \Sigma) = - \frac{1}{2}\log_{10}\left((Y - X\hat B)^T\hat \Sigma^{-1}(Y - X\hat B)\right) - n\log_{10}(2\pi) - \log_{10}|\hat \Sigma|
\label{eq:loglik}
$$

@@

$$
LOD = \log_{10} \left(\frac{\max_{\lambda_1, \lambda_2}L(B, \Sigma, \lambda_1, \lambda_2)}{\max_{\lambda}L(B, \Sigma, \lambda, \lambda)} \right)
\label{eq:lrt}
$$

$$
ll(\lambda_1, \lambda_2)
$$

@@

$$
Y = \alpha 1 + WC + E
\label{model1}
$$

$$
Y = XB + WC + E
\label{model2}
$$

$$
Y = \alpha 1 + WC + M\beta + E
\label{model3}
$$

$$
Y = XB + WC + M\beta + E
\label{model4}
$$

@@

scols_pre <- scols_extra %>%
  dplyr::select(n_med_per_local$local_symbol)
# get ordering for columns of scols_pre
col_order <- scols_pre %>%
  t() %>%
  dist() %>%
  hclust() %>%
  as.dendrogram() %>%
  dendextend::seriate_dendrogram(dist(t(scols_pre))) %>%
  order.dendrogram()
scols <- scols_pre[ , col_order] %>%
  mutate(local = scols1)
fnhtml <- here("analysis", "figures", paste0("Chr", hot_chr, "hm.html"))
```

```{r heat9-2, eval = !file.exists(fnhtml)}
ord <- match(rn, rownames(pm))

p <- pm[ord, ord] %>%
  apply(FUN = trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply(Rowv = FALSE,
            Colv = FALSE,
            cexRow = 0.2,
            cexCol = 0.2,
            symm = TRUE,
            row_side_colors = scols[ord, ],
            col_side_colors = tibble(local = scols1[ord]),
            limits = c(0, 5)
            ) %>%
  hide_guides()
fnpdf <- here("analysis", "figures", paste0("Chr", hot_chr, "hm.pdf"))
htmlwidgets::saveWidget(widget = p,
                        file = fnhtml
                        )
webshot::webshot(url = fnhtml,
                 file = fnpdf,
                 cliprect = "viewport"
                 )
```

```{r heat10-2}
webshot::webshot(fnhtml)
```

@@

```{r heat9-5, ref.label = "heat9-2", eval = !file.exists(fnhtml)}
```

```{r heat10-5, ref.label="heat10-2"}
```

@@

```{r heat9-7, ref.label = "heat9-2", eval = !file.exists(fnhtml)}
```

```{r heat10-7, ref.label="heat10-2"}
```

@@

```{r heat9-11, ref.label = "heat9-2", eval = !file.exists(fnhtml)}
```

```{r heat10-11, ref.label="heat10-2"}
```

@@

```{r heat9-13, ref.label = "heat9-2", eval = !file.exists(fnhtml)}
```

```{r heat10-13, ref.label="heat10-2"}
```

@@
